%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bruno Saboia de Albuquerque CV template
% LaTeX Template
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%------------------------------------------------------------------------------

\documentclass[margin]{res} % Use the res.cls style

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,
	urlcolor=cyan,
	pdftitle={Bruno Saboia de Albuquerque - CV},
	pdfpagemode=FullScreen,
}

\usepackage{helvet}

\setlength{\textwidth}{5.2in} %default 5.1in % Text width of the document

\begin{document}
	%------------------------------------------------------------------------------
	%	NAME, ADDRESS AND SOCIAL NETWORK SECTION
	%------------------------------------------------------------------------------
	\moveleft.5\hoffset\centerline{\huge\bf Bruno Saboia de Albuquerque}
	\moveleft\hoffset\vbox{\hrule width\resumewidth height 1.5pt}
	\moveleft.5\hoffset\centerline{Aeschengraben 17, 4051 Basel, CH}
	\moveleft.5\hoffset\centerline{e-mail: bruno@saboia.it -- Tel: +41 78 245 7688}
	\moveleft.5\hoffset\centerline{{\sl{\href{https://github.com/brunosaboia}{GitHub} -- \href{https://linkedin.com/in/brunosaboia}{LinkedIn}}}}

	\begin{resume}
		%------------------------------------------------------------------------------
		% EXPERIENCE
		%------------------------------------------------------------------------------
		\section{EXPERIENCE}
		{\bf Bank for International Settlements}, {\sl Basel, CH} \hfill {\sl May 2024 - May 2025} \\
		{\sl — \href{https://bis.org}{https://bis.org}} \\
		{\sl Data Analytics Engineer} \\
		\\
		The BIS (Bank for International Settlements) is the bank for central banks. Its mission is to support central banks' pursuit of monetary and financial stability through international cooperation.

		My mission is to work with AI-related projects, mainly working on BIS GPT, an LLM-based chatbot compliant with the security and privacy requirements needed by the bank.

		{\sl Technologies: TypeScript, React, Python, LLM, RAG, Azure, OpenShift, Docker, ArgoCD, GitHub }\\

		{\bf Bank for International Settlements}, {\sl Basel, CH} \hfill {\sl May 2022 - May 2024} \\
		{\sl — \href{https://bis.org}{https://bis.org}} \\
		{\sl Business Analyst/Developer} \\
		\\
		The BIS (Bank for International Settlements) is the bank for central banks. Its mission is to support central banks' pursuit of monetary and financial stability through international cooperation.

		My mission was to help the Risk Management department to understand the different aspects of financial risk that the bank is incurring, using best IT practices to do so.

		{\sl Technologies: C\#, Git, Azure DevOps, Python, PowerShell, Bash, OpenShift, SQL, Octopus, ArgoCD }\\

		{\bf Clevertech}, {\sl Remote (Brazil -- US)} \hfill {\sl March 2022 - May 2022} \\
		{\sl — \href{https://clevertech.biz}{https://clevertech.biz}} \\
		{\sl Senior Software Engineer} \\
		\\
		Clevertech is an American IT company, providing consulting services for large customers around the globe.

		My mission was to help customers implementing the best solutions they can in their projects, giving them insights and planning on how to build better software. I also wrote Python code and SQL queries.

		{\sl Technologies: Python, Apache Airflow, Postgres} \\

		{\bf Tesseract}, {\sl Remote (Brazil -- Finland)} \hfill {\sl September 2021 - March 2022} \\
		{\sl — \href{https://tesseractinvestment.com/}{https://tesseractinvestment.com/}} \\
		{\sl Full-stack developer} \\
		\\
		Tesseract is a Finnish startup which borrows cryptocurrencies, matchmaking investors and lenders. It is Fin-FSA regulated digital asset innovator, backed by reputable investors, focusing on institutional brokerage and asset management.

		My mission was to enhance the infrastructure using IaC (Infrastructure as Code).

		{\sl Technologies: Pulumi, TypeScript, GitHub Actions} \\

		{\bf BEC Financial Technologies}, {\sl Roskilde, Denmark} \hfill {\sl April 2021 - September 2021} \\
		{\sl — \href{https://bec.dk}{https://bec.dk}} \\
		{\sl Senior Software Engineer} \\
		\\
		BEC is a Danish fintech that provides services for medium-to-small banks. Founded in 1964, is one of the main back-bones of IT services for financial companies in the Nordic country.

		My mission was to enable developers to use the Event Streaming Platform as efficiently as possible.

		{\sl Technologies}: Kafka, Java, Bash, OpenShift, Git, CDC, Docker, Jenkins\\

		{\bf Danske Bank}, {\sl Copenhagen, Denmark} \hfill {\sl February 2019 - March 2021} \\
		{\sl — \href{https://danskebank.dk}{https://danskebank.dk}} \\
		{\sl Senior Software Engineer} \\
		\\
		Danske Bank A/S is a Danish multinational banking and financial services corporation, founded in 1871.

		My mission was create a new corporate solution to search for payment, named SmartSearch. I was also involved with other tasks and projects.

		{\sl Technologies: Kubernetes, DB2, C\#, Jenkins, .NET Core, COBOL, Kafka, Java, Kotlin, Rust, ELK stack }  \\

		{\bf Coinify ApS}, {\sl Copenhagen, Denmark} \hfill {\sl August 2017 - January 2019} \\
		{\sl — \href{https://coinify.com}{https://coinify.com}} \\
		{\sl Senior Software Engineer} \\
		\\
		Coinify is a Nordic startup which enables merchants to accept cryptocurrencies in exchange for their goods and services, either in mortar-and-brick or online stores. The company also provides a cryptocurrency trading platform.

		My mission was to develop new features and improve existing ones, as well as fixing bugs.

		{\sl Technologies: Node.js, TypeScript, Docker, AWS, PHP, HTML/CSS } \\

		{\bf AH Integration Solutions AS}, {\sl Remote (Brazil -- Norway)} \hfill {\sl February 2017 - August 2017} \\
		{\sl — \href{https://web.archive.org/web/20160208120600/http://ahint.no/}{http://ahint.no/} (archived)} \\
		{\sl Consultant} \\
		\\
		AH Integrations was a Norwegian company working in the health sector.

		My mission was to act as a development consultant, helping the team to make decisions regarding tech choices, while performing coding tasks.

		{\sl Technologies: C\#, WPF, Crystal Reports } \\

		{\bf ITOUCH TECH}, {\sl Fortaleza, Brazil} \hfill {\sl July 2015 - February 2017} \\
		{\sl — \href{https://itouchtech.us}{https://itouchtech.us}} \\
		{\sl CTO} \\
		\\
		ITOUCH TECH is an US-based company which providers FFLs with a digital way to fill ATF4473 forms.

		My mission was to design and implement the systems, migrating their old solution to more modern technologies, as well as deploying them to the customer stores.

		{\sl Technologies: C\#, Windows Forms, WPF, Octopus } \\

		{\bf HBS}, {\sl Fortaleza, Brazil} \hfill {\sl April 2014 - July 2014} \\
		{\sl — \href{https://hbs.tv}{https://hbs.tv}} \\
		{\sl IT Specialist -- contract} \\
		\\
		Founded in 1999, Host Broadcast Services (HBS) was originally established with the core mandate of being the Host Broadcaster (HB) for the 2002 FIFA World Cup Korea/Japan™; the organisation has since developed as a renowned host broadcast expert.

		This was a temporary contract, taking place during the FIFA World Cup in Brazil.

		My mission was to aid HBS to have a stable, smooth and reliable IT site, so it could broadcast the FIFA World Cup to the entire world.

		{\sl Technologies: AD, Windows Server, C\#, VB, satellite comm, optical fiber } \\

		{\bf Predictive Science}, {\sl Remote (Brazil -- US)} \hfill {\sl January 2013 - March 2014} \\
		{\sl — \href{https://predsci.com}{https://predsci.com}} \\
		{\sl Senior Software Engineer } \\
		\\
		Predictive Science Inc. is an employee-owned company that delivers state-of-the-art scientific solutions.

		My mission was to develop a system to Verizon to aid the ERT (Executive Response Team) to make informed decisions about customer issues.

		{\sl Technologies: Python, Kafka, C\#} \\

		{\bf Upstream Systems}, {\sl Athens, Greece} \hfill {\sl July 2012 - December 2012} \\
		{\sl — \href{https://www.upstreamsystems.com}{https://www.upstreamsystems.com}} \\
		{\sl IT Specialist/Copywriter } \\
		\\
		Upstream Systems is a Greek media company that helps mobile carriers to promote products and services to their customers.

		My mission was to help copywriters to track their work, as well as copywriting in Brazilian Portuguese for Brazilian mobile carriers.

		{\sl Technologies: Excel, VBA } \\

		{\bf Procuradoria Geral do Estado do Ceará - PGECE}, {\sl Fortaleza, Brazil} \hfill {\sl March 2011 - December 2011} \\
		{\sl — \href{https://pge.ce.gov.br}{https://pge.ce.gov.br}} \\
		{\sl Senior Software Engineer } \\
		\\
		PGE is the state attorney central for the state of Ceará, in Brazil.

		First, my mission was to aid PGE on its goal to migrate to the digital judiciary process, which was then deemed as necessary by Brazilian Supreme Court.

		After a promotion, my mission was to create PGE-C2, a cloud-based Android app that would be used for the daily operation of the attorneys.

		{\sl Technologies: Ruby, Rails, C\#/Mono, Postgres, Solr, Android, Java } \\

		{\bf SecrelNET}, {\sl Fortaleza, Brazil} \hfill {\sl January 2009 - Dec 2011} \\
		{\sl — \href{https://secrelnet.com.br}{secrelnet.com.br}} \\
		{\sl Senior Software Engineer } \\
		\\
		SecrelNET is an ISP of Fortaleza, Brazil. It was one of the pioneers of both dial-up and broadband technologies in the area.

		My mission was to create Spider, a project to automate tasks which before its implementation required a human operator (such as creating accounts, websites, directories for hosting purposes, and many more).

		{\sl Technologies: .NET, Java, C, Windows Development, WMI, VB, Linux, Hyper-V, Active Directory } \\

		%------------------------------------------------------------------------------
		% EDUCATION
		%------------------------------------------------------------------------------
		\section{EDUCATION}
		% \vspace{-.4cm}
		{\bf Universidade Federal do Ceará} \hfill {\sl 2013 - 2016}\\
		{\bf UFC}, {\sl Fortaleza, Brazil}  \\
		{\sl — \href{https://ufc.br}{https://ufc.br}} \\
		{\sl Bachelor of Science}  \\
		Economics (\href{https://saboia.it/assets/pdf/transcripts/2016-04-29-transcript-ufc.pdf}{Transcript of records})

		{\bf Universität Liechtenstein} \hfill {\sl 2015 - 2016}\\
		{\bf UNILI}, {\sl Vaduz, Liechtenstein}  \\
		{\sl — \href{https://uni.li}{https://uni.li}} \\
		{\sl Exchange Student (Winter Semester)}  \\
		Business Administration and IT (\href{https://saboia.it/assets/pdf/transcripts/2016-02-17-transcript-liech.pdf}{Transcript of records})
		\\

		%------------------------------------------------------------------------------
		% PUBLICATIONS
		%------------------------------------------------------------------------------
		\section{PUBLICATIONS}
		\begin{itemize}
			\item {\sl Over the Cliff: How Brazil’s 2004–2016 Business Cycle Became Its Worst Recession in a Century} (2020), DOI: \href{https://doi.org/10.35297/qjae.010027}{10.35297/qjae.010027}
			\item {\sl Understanding Bitcoins: Facts and Questions} (2015), DOI: \href{https://doi.org/10.5935/0034-7140.20150001}{10.5935/0034-7140.20150001}
		\end{itemize}
		\hfill
		%------------------------------------------------------------------------------
		% REVIEWS
		%------------------------------------------------------------------------------
		\section{REVIEWS}
		{\bf Bachelor thesis:}
		\begin{itemize}
			\item {\sl Os efeitos do grau de Liberdade Econômica sobre o Índice de Desenvolvimento Humano (IDH) e o IDH ajustado à desigualdade}, Renato Leitão (\href{https://saboia.it/assets/pdf/reviews/2022-02-15-renato-leitao.pdf}{2022})
			\item {\sl Bitcoins - uma moeda global e descentralizada}, Raíssa Guerra (\href{https://saboia.it/assets/pdf/reviews/2022-02-15-raissa-guerra.pdf}{2022})
			\item {\sl Abertura comercial e produtividade: evidências empíricas de correlação nas últimas duas décadas}, Saulo Queiroz (\href{https://saboia.it/assets/pdf/reviews/2021-08-26-saulo-queiroz.pdf}{2021})
			\item {\sl Mercado de criptoativos: conjuntura e desafios}, Gabriel Radaelly (\href{https://saboia.it/assets/pdf/reviews/2021-08-25-gabriel-radaelly.pdf}{2021})
			\item {\sl A moeda digital do século XXI: um estudo de caso sobre o Bitcoin}, Hemerson Braga (\href{https://saboia.it/assets/pdf/reviews/2022-07-07-hemerson-braga.pdf}{2021})
		\end{itemize}
		{\bf Papers:}
		\begin{itemize}
			\item {\sl The Political Thought of José Osvaldo de Meira Penna}, Gabriel F. Benzecry, (\href{https://jls.mises.org/article/70305-the-political-thought-of-jose-osvaldo-de-meira-penna}{2023})
		\end{itemize}
		\hfill

		%------------------------------------------------------------------------------
		% AWARDS
		%------------------------------------------------------------------------------
		\section{AWARDS}
		\begin{itemize}
			\item {\sl SAP DemoJam Barcelona}, 1st place (\href{https://www.uni.li/en/topics/information-systems/news/university-students-successful-in-world2019s-leading-sap-conference}{2015})
		\end{itemize}
		\hfill

		%------------------------------------------------------------------------------
		% CERTIFICATIONS
		%------------------------------------------------------------------------------
		\section{CERTIFICATIONS}
		\begin{itemize}
			\item {\sl Machine Learning, } (\href{https://www.coursera.org/api/legacyCertificates.v1/spark/statementOfAccomplishment/152~314678/pdf}{2013})
			\item {\sl Computational Investing, Part I } (\href{https://www.coursera.org/api/legacyCertificates.v1/spark/statementOfAccomplishment/364~314678/pdf}{2013})
		\end{itemize}
		\hfill

		%------------------------------------------------------------------------------
		% SKILLS
		%------------------------------------------------------------------------------
		\section{SKILLS}
		{\bf Programming-related skills (in years of experience):}
		\begin{itemize}
			\item {\sl C\#}, 20+
			\item {\sl Python}, 20+
			\item {\sl SQL} 20+,
			\item {\sl Bash/Shell} 15+,
			\item {\sl JavaScript}, 5
			\item {\sl TypeScript}, 3
			\item {\sl Ruby}, 3
			\item {\sl React}, 1
		\end{itemize}
		{\bf Technologies (in years of experience):}
		\begin{itemize}
			\item {\sl DevOps } 10+
			\item {\sl CI/CD } 10+
			\item {\sl AI (Artificial Intelligence)}, 6
			\item {\sl ML (Machine Learning)}, 5
			\item {\sl LLM (Large Language Models)}, 2
			\item {\sl RAG  (Retrieval Augmented Generation)}, 1
		\end{itemize}
		{\bf Languages:}
		\begin{itemize}
			\item {\sl Portuguese}, Native
			\item {\sl English}, Full professional proficiency
			\item {\sl Spanish}, Limited professional proficiency
			\item {\sl German}, Basic
			\item {\sl Italian}, Basic
			\item {\sl Danish}, Basic
			\item {\sl Hebrew}, Basic
		\end{itemize}
		{\bf Other skills:}
		\begin{itemize}
			\item {\sl OS (Linux, Windows, macOS)}, Advanced
			\item {\sl Office Suite (Word, PowerPoint, Excel (with VBA))}, Advanced
			\item {\sl Networking}, Intermediate
			\item {\sl OCP/K8S}, Intermediate
			\item {\sl \LaTeX}, Intermediate
			\item {\sl R/Matlab/Octave}, Intermediate
			\item {\sl AutoCAD}, Intermediate
			\item {\sl Photoshop/Image editing tools}, Basic
		\end{itemize}
		\hfill
		\section{HOBBIES}
		{\bf Sports:}
		\begin{itemize}
			\item {\sl Go-karting}
			\item {\sl Martial arts}
		\end{itemize}
		{\bf Music:}
		\begin{itemize}
			\item {\sl Singing}
			\item {\sl Guitar}
			\item {\sl Piano}
		\end{itemize}
		{\bf Research:}
		\begin{itemize}
			\item {\sl Genealogy}
			\item {\sl History}
			\item {\sl Mathematics}
			\item {\sl Physics}
		\end{itemize}
		{\bf Other:}
		\begin{itemize}
			\item {\sl Motorbike}
			\item {\sl Photography}
			\item {\sl Writing}
		\end{itemize}
	\end{resume}
	\vfill
	\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.4pt}
	\moveleft.5\hoffset\centerline{\footnotesize{Last updated at $LAST_UPDATED$ -- the most recent copy can be found at \href{https://bruno.saboia.it/cv}{https://bruno.saboia.it/cv}}}
\end{document}
